---
title: "Presentation_v2"
subtitle: Johanna Haraldsdottir (s204657), Marie Kragh (s203566), Sofie Bruun (s194678), Amalie Schultz-Nielsen (s204643) and Malou Bech Jakobsen (s203515)
format:
  revealjs:
    width: 1800  # Increase the width of slides (default is ~960)
    height: 900  # Keep the height proportional
    margin: 0.05
    embed-resources: true
---

## Introduction

::: columns
::: {.column width="40%"}
-   The Drug data set provides information about various types of medications ranging from treatments of cancer, Alzheimer's disease, and bacterial infections to more simple symptomatic drugs in treating dry cough, common colds, and for pain relief.

-   Variables: Medicine name, composition, Uses, side effects, manufacturer as well as how many poor, average and excellent reviews (%)
:::

::: {.column width="60%"}
```{r}
rm(list=ls())
library("tidyverse")
library("purrr")
library("broom")
library("readr")
library("here")
library("knitr")


data <- read_tsv(here("data/01_dat_load.tsv"))

data |>
  select(`Medicine Name`, Uses) |>
  print()
```
:::
:::

## Materials and Methods

::: columns
::: {.column width="50%"}
### Cleaning

```{r, }

image_path <- here("results", "flow_clean.png")

include_graphics(image_path)
```
:::

::: {.column width="50%"}
### Augmentation

```{r}

image_path <- here("results", "flow_aug.png")

include_graphics(image_path)
```
:::
:::

## Results Analysis One

::: columns
::: {.column width="50%"}
### Title

```{r}

image_path <- here("results", "Scatter_Side_Effects_Review_all.png")
 
include_graphics(image_path)

```
:::

::: {.column width="50%"}
### Title

```{r}
image_path <- here("results", "boxplot_Excellent_Administration_type.png")

include_graphics(image_path)
```
:::
:::

## Results Analysis Two

::: columns
::: {.column width="50%"}
```{r}

image_path <- here("results", "Most_prevalent_medicines_plot.png")

# Include the image in the document
include_graphics(image_path)
# 
# image_path <- here("results", "Most_prevalent_medicines_plot.png") 
# 
# include_graphics(image_path)
```
:::

::: {.column width="50%"}
```{r}
image_path <- here("results", "Side_Effects_Administration_type.png") 

include_graphics(image_path)
```
:::
:::

## Results Analysis Three

::: columns
::: {.column width="50%"}
skriv bullets points
:::

::: {.column width="50%"}
```{r}
image_path <- here("results", "Manufacturers_bar_plot.png")  

include_graphics(image_path)
```
:::
:::

## 

## Discussion

::: columns
::: {.column width="50%"}
### Keep in Mind

-   Representativeness of data
:::

::: {.column width="50%"}
### The Next Steps

-   Augmentation: New administration type categories \[Topical, Oral, Parenteral\]

-   Analysis of the cancer types
:::
:::

## 
