---
title: "Cancer Medicine Data Project"
subtitle: Johanna Haraldsdottir (s204657), Marie Kragh (s203566), Sofie Bruun (s194678), Amalie Schultz-Nielsen (s204643), and Malou Bech Jakobsen (s203515)
format:
  revealjs:
    width: 1800  # Increase the width of slides (default is ~960)
    height: 900  # Keep the height proportional
    margin: 0.05
    theme: solarized
    embed-resources: true
---

## Introduction

::: columns
::: {.column width="50%"}
-   The Drug data set provides information about various medications: from treatments of cancer and Alzheimer's disease to common colds and pain relief

-   Purpose: Assist healthcare professionals and patients in making decisions when choosing a medication

-   The 3 rules for making a data set tidy are not satisfied
:::

::: {.column width="50%"}
```{r}
rm(list=ls())
library("tidyverse")
library("purrr")
library("broom")
library("readr")
library("here")
library("knitr")


data <- read_tsv(here("data/01_dat_load.tsv"))

data |>
  select(`Medicine Name`, Uses, Composition) |>
  print()
```
:::
:::

## Materials and Methods

::: columns
::: {.column width="50%"}
### Cleaning

```{r, }

image_path <- here("results/Images", "flow_clean.png")

include_graphics(image_path)
```
:::

::: {.column width="50%"}
### Augmentation

```{r}

image_path <- here("results/Images", "flow_aug.png")

include_graphics(image_path)
```
:::
:::

## Description of the Cancer Data

::: columns
::: {.column width="50%"}
-   **Variables:**\
    Medicine name\
    Composition\
    Uses\
    Side effects\
    Manufacturer\
    Poor, Average, Excellent reviews (%)

-   Distribution of Side Effects
:::

::: {.column width="50%"}
### Hej

```{r}
library("tidyverse")
library("readr")
library("here")
source("99_proj_func.R")

image_path <- here("results", "Frequency_of_Unique_Drugs_plot.png")

# Include the image in the document
include_graphics(image_path)

# cancer_data <- read_tsv(here('data/03_dat_aug.tsv'))

# SummaryStatistics(cancer_data, Count_Side_Effects)
```
:::
:::

## Analysis 1: Review Levels

::: columns
::: {.column width="100%"}
What are the probable causes behind the excellent, average, and poor reviews for the cancer drugs?
:::

::: {.column width="50%"}
### Influence of Number of Side Effects

```{r}

image_path <- here("results", "Scatter_Side_Effects_Review_all.png")
 
include_graphics(image_path)

```
:::

::: {.column width="50%"}
### Influence of Administration Type

```{r}
image_path <- here("results", "boxplot_Excellent_Administration_type.png")

include_graphics(image_path)
```
:::
:::

## Analysis 2: The 10 most prevalent medications

::: columns
::: {.column width="50%"}
### Number of Side Effects for the 8 most prevalent drugs

```{r}

image_path <- here("results", "Most_prevalent_medicines_plot.png")

# Include the image in the document
include_graphics(image_path)
# 
# image_path <- here("results", "Most_prevalent_medicines_plot.png") 
# 
# include_graphics(image_path)
```
:::

::: {.column width="50%"}
### Number of side effects for a specific administration type

```{r}
image_path <- here("results", "Side_Effects_Administration_type.png") 

include_graphics(image_path)
```
:::
:::

## Analysis 3: Manufacturer and API in relation to review classifications

::: columns
::: {.column width="50%"}
skriv bullets points
:::

::: {.column width="50%"}
```{r}
image_path <- here("results", "Manufacturers_bar_plot.png")  

include_graphics(image_path)
```
:::
:::

## Conclusion

::: columns
::: {.column width="75%"}
-   There was no apparent tendency between the number of side effects and what type of review the specific drug got

-   The review levels do not seem to be dependent on the type of administration

-   The distribution of side effects seem random for different administration types for the 8 most prevalent drugs, although a rather high number of side effects are present for these drugs

-   The 8 most prevalent drugs only have the administration types injection and tablet, 75% being injection

-   Administration through capsules is associated with a high number of side effects whereas administrations such as cream and lotion are associated with a very low number or no side effects.
:::
:::

## Discussion

::: columns
::: {.column width="50%"}
### Keep in Mind

-   Representativeness of data
:::

::: {.column width="50%"}
### The Next Steps

-   Augmentation: New administration type categories \[Topical, Oral, Parenteral\]

-   Analysis of the cancer types

-   Analyzing other variables: Influence of API and number of applications

-   
:::
:::

## 
