---
title: "04_describe"
format: html
editor: visual
---

## Loading libraries and data

```{r}
dir_load <- here("/data")
# Specify the file path with the new name
file_path <- file.path(dir_load, "03_dat_aug.tsv")

# Save the dataframe as a CSV file
write.tsv(aug_clean_data, file_path, row.names = FALSE)
```

## Descriptive statistics of the data

The data is introduced after both cleaning and augmentation have been performed. The aim is to introduce descriptive statistics in regards to distribution of classes in the different variables.

#### Dimentionality

Firstly, the dimensionality is investigated to get an idea of the size.

```{r}
# Checking for dimensionality of dataset 
data |> 
  dim_desc()

```

#### Variable and class distirbution

-   hvor mange NA optræder for forskellige variable

```{r}

```

-   Beregne means hvor general gentagelse af drugs

```{r}

```

-   plotte hvor mange gange hver drug går i gen (plot)

```{r}

```

-   gennemsnit sideffect for hver drug

```{r}

```

-   hvor mange gange går applications igen (plot)

```{r}

```

-   unikke antal type af medicn

```{r}

```

-   antal af gange administration type går igen (plot)

```{r}

```

### Bonus

-   hvor mange gange kan et bestemt drug f.eks. behandle kræft (eller anden sygdom) - her kan application bruges

#### 
