---
title: "04_describe"
format: html
editor: visual
---

## Loading libraries and data

```{r}
dir_load <- here("/data")
# Specify the file path with the new name
file_path <- file.path(dir_load, "03_dat_aug.tsv")

# Save the dataframe as a CSV file
write.tsv(aug_clean_data, file_path, row.names = FALSE)
```

## Descriptive statistics of the data

The Drug data set provides information about various types of medications ranging from treatments of cancer, Alzheimer's disease, and Bacterial infections to more simple symptomatic drugs in treating dry cough, pain relief, and common colds.

The data set investigates the composition, administration type, applications, and side effects of the different medications. Furthermore, the drugs are reviewed by the user and split into poor, average, and excelent reviews by percentages.

The purpose of the data is to assist healthcare professionals and patients in making decisions when choosing/using a medication. Therefore, the description and analysis of the data focuses on this perspective and introduces plots that can further aid in this aim.

The data is introduced after both cleaning and augmentation have been performed. The aim of this section is to introduce descriptive statistics in regards to distribution of classes in the different variables.

#### Dimensionality

Firstly, the dimensionality of the data set is investigated to get an idea of its size.

```{r}
# Checking for dimensionality of dataset 
data |> 
  dim_desc()

```

#### Variable and class distirbution

-   hvor mange NA optræder for forskellige variable

```{r}
NA_observations <- clean_data |> 
  select() |>
  filter(is.na())

print(NA_observations)
```

-   Beregne means hvor general gentagelse af drugs

```{r}
### 
clean_data |> 
  select(variable) |>
  summarise(x_mu = mean(x), x_max = max(x))



```

-   plotte hvor mange gange hver drug går igen (plot)

```{r}

```

-   gennemsnit sideffect for hver drug

```{r}

```

-   hvor mange gange går applications igen (plot)

```{r}

```

-   unikke antal type af medicin

```{r}

```

-   antal af gange administration type går igen (plot)

```{r}

```

### Bonus

-   hvor mange gange kan et bestemt drug f.eks. behandle kræft (eller anden sygdom) - her kan application bruges

#### 
