---
title: "04_describe"
format: html
editor: visual
---

## Loading libraries and data

### Loading libraries

Loading the relevant libraries.

```{r}
rm(list=ls())
library("tidyverse")
library("dplyr")
library("readr")
```

### Loading long format augmented clean data

```{r}
#| message: false

# Loading the clean data tsv file 
aug_clean_data <- read_tsv(here('data/03_dat_aug.tsv'))
```

## Descriptive statistics of the data

The Drug data set provides information about various types of medications ranging from treatments of cancer, Alzheimer's disease, and Bacterial infections to more simple symptomatic drugs in treating dry cough, pain relief, and common colds.\
The types of medications vary greatly, therefore this project will only be investigating drugs applicable for the treatment of cancer. This will streamline the project and make it easier to make concrete conclusions.

The raw data set investigates the composition, administration type, applications, and side effects of the different medications. Furthermore, the drugs are reviewed by the user and split into poor, average, and excellent reviews by percentages.

The purpose of the data is to assist healthcare professionals and patients in making decisions when choosing/using a medication. Therefore, the description and analysis of the data focuses on this perspective and introduces plots that can further aid in this aim.

The data is introduced after both cleaning and augmentation have been performed. The aim of this section is to introduce descriptive statistics in regards to distribution of classes in the different variables.

#### Dimensionality

Firstly, the dimensionality of the data set is investigated to get an idea of its size.\
The number of variables is shown and a view of the data is given.

```{r}
# Checking for dimensionality of dataset 
aug_clean_data |> 
  dim_desc()

# Finding number of variables
aug_clean_data |> 
  length()

# Showing the data 
aug_clean_data |> 
  View()

```

### Investigating number of unique cancer types

It is interesting to look at how many different cancer types there is in the data set and what types it is.

```{r}
# Find unique types of cancer from the Application_type variable
unique_cancer_rows <- aug_clean_data |>
  select(Application_type) |>
  filter(str_detect(Application_type, regex("cancer", ignore_case = TRUE))) |>
  # Getting the unique types
  distinct() 

# Number of different cancer types
unique_cancer_rows |>
  dim_desc()

# Overview of the cancer types
View(unique_cancer_rows)

```

-   Beregne means hvor general gentagelse af drugs

```{r}
### 
clean_data |> 
  select(variable) |>
  summarise(x_mu = mean(x), x_max = max(x), x_min = min(x), )



```

-   plotte hvor mange gange hver drug går igen (plot)

```{r}



```

-   gennemsnit sideffect for hver drug

```{r}


```

-   hvor mange gange går applications igen (plot)

```{r}

```

-   unikke antal type af medicin

```{r}



```

-   antal af gange administration type går igen (plot)

```{r}

```

### Bonus

-   hvor mange gange kan et bestemt drug f.eks. behandle kræft (eller anden sygdom) - her kan application bruges

#### 
