## Analysis of Review Classification

This analysis aims to investigate whether the manufacturer or API has relation to specific review classifications. The top six of each variable are chosen to enable a meaningful and interpretative visualization.

Firstly, the environment is cleared and libraries and the augmented data set is loaded.

```{r, warning=FALSE}
#| message: false

# Clearing environment
rm(list=ls())

# Loading libraries
library("tidyverse")
library("dplyr")
library("readr")
library("here")

# Loading the augmented data tsv file 
cancer_data <- read_tsv(here('data/03_dat_aug.tsv'))
```

### Influence of Manufacturer

An interesting relation to investigate is if the top six manufacturers have a certain distribution across its reviewed products. The top six manufacturers are those with the most products in the data set. The distribution of review classifications of the products that each manufacturer produces is shown in a bar plot.

```{r}
# Step 1: Get the top 6 manufacturers with the most products
top_manufacturers <- cancer_data |> 
  distinct(ID,   # Only have one row for each product
           .keep_all = TRUE) |> 
  group_by(Manufacturer) |>
  summarise(product_count = n()) |>   # Count the number of products for each manufacturer
  arrange(desc(product_count)) |>   # Sort by the product count in descending order
  slice_head(n = 6)  # Select the top 6 manufacturers


# Step 2: Retaining only the rows in orignal cancer data set where manufacturer is one of the top 6 manufacturers
cancer_data_selected <- cancer_data |> 
  distinct(ID,
           .keep_all = TRUE) |> 
  semi_join(top_manufacturers, 
            by = "Manufacturer")

# Step 3: Reorder Classification_Review factor to ensure "Average" is the middel bar
cancer_data_selected <- cancer_data_selected |> 
  mutate(Classification_Review = factor(Classification_Review, 
                                       levels = c("Poor", 
                                                  "Average", 
                                                  "Excellent")))
# Step 4: Create bar plot
Manufacturers_bar_plot <- cancer_data_selected |> 
  ggplot(aes(x = Classification_Review, 
             fill = Classification_Review)) +
    geom_bar(stat = "count", 
             show.legend = TRUE) + 
    facet_wrap(~ Manufacturer) + 
    scale_fill_manual(values = c("Poor" = "#F8766D",  # Making sure color match meaning
                                 "Average" = "#619CFF",
                                 "Excellent" = "#00BA38")) +
    labs(x = '',
         y = "Number of Products", 
         title = str_wrap("Distribution of Review Classification of Products from Top Six  Manufacturers", 55),
         fill= "Review Classification") +
    theme_minimal() +
    theme(axis.text.x=element_blank(),
          legend.position = 'bottom')  

# Saving the plot
ggsave(here("results/Manufacturers_bar_plot.png"), plot = Manufacturers_bar_plot, width = 6, height = 4)

print(Manufacturers_bar_plot)
```

From the bar plot it can be seen that there is no apparent correlation between being one of the top producers and having a higher number of excellent reviews. Lupin Ltd and Wockhardt Ltd has the most products with poor reviews. Oppositely, Sun Pharmaceuticals Industries Ltd has most products with excellent reviews. The distribution of the different reviews seems to be random across the top six manufacturers. The distribution of review classifications seems to be random across the top six manufacturers.

### Influence of API

In a similar manner the top six used APIs were investigated. Perhaps there is a correlation between being widely used and having good reviews. The bar plot below shows the distribution of reviews for products that includes the top six APIs.

```{r}
# Step 1: Get the top 6 most used APIs
top_API <- cancer_data |> 
  filter(!is.na(API_name)) |>   # Exclude rows where API_name is NA
  distinct(ID,   # Only have one row for each product
           .keep_all = TRUE) |> 
  group_by(API_name) |>   # Group by API_name
  summarise(API_count = n()) |>   # Count the number of products for each API
  arrange(desc(API_count)) |>   # Sort by API count in descending order
  slice_head(n = 6)  # Select the top 6 APIs

# Step 2: Retaining only the rows in orignal cancer data set where API is one of the top 6 used APIs and filtering out any missing API names
cancer_data_selected <- cancer_data |> 
  distinct(ID,   # Only have one row for each product
           .keep_all = TRUE) |> 
  semi_join(top_API, by = "API_name") |> 
  filter(!is.na(API_name))  # Exclude NA API names


# Step 3: Reorder Classification_Review factor to ensure "Average" is the middel bar
cancer_data_selected <- cancer_data_selected |> 
  mutate(Classification_Review = factor(Classification_Review, 
                                       levels = c("Poor", 
                                                  "Average", 
                                                  "Excellent")))
# Step 4: Create the bar plot
API_bar_plot <-   cancer_data_selected |> 
  ggplot(aes(x = Classification_Review, 
             fill = Classification_Review)) +
    geom_bar(stat = "count", 
             show.legend = TRUE) + 
    facet_wrap(~ str_wrap(API_name, width = 30)) +  # Create a facet for each API_name
    scale_fill_manual(values = c("Poor" = "#F8766D",   # Making sure color match meaning
                                 "Average" = "#619CFF",
                                 "Excellent" = "#00BA38")) +
    labs(x = "", 
         y = "Number of Products", 
         title = "Distribution of Review Classification of Top Six Used APIs",
         fill = "Review Classification") +
    theme_minimal() +  # Apply a minimal theme
    theme(axis.text.x = element_blank(),
          legend.position = 'bottom')
          
# Saving the plot          
ggsave(here("results/API_bar_plot.png"), plot = API_bar_plot, width = 6, height = 4)

print(API_bar_plot)
```

Once again, it seems there is a random distribution of review classification of the top six most used drugs in the cancer data set. Interestingly, the Recombinant Human Erythropoietin Alfa, which is the top 1 API, has mostly poor and least excellent reviews. Actually, 3 out of 6 APIs has the majority of reviews as poor. Only Leuprolide has excellent as the largest review classifications.

All in all, neither manufacturer or API seems shows a tendency in regards to review classification distribution of products from the cancer data set. The conclusion might be different, when looking at the entire data set, while more difficult to visualize and interpret.
