---
title: "05_analysis_3"
format: html
editor: visual
---

## Loading library

```{r}
rm(list=ls()) 
library("tidyverse") 
library("dplyr") 
library("readr")
library('ggplot2')
```

## Loading cancer data file

```{r}
# Loading the cleaned and augmented file:  
cancer_data <- read_tsv(here('data/03_dat_aug.tsv')) 
```

# Analysis of the 10 most prevalent medicines

A subset of the cancer data is made to investigate only the 10 most prevalent medicines, found from the descriptive statistics. These 10 medicines are chosen as these are the only ones exceeding 2% prevalence in the data set.

The analysis aims to investigate potential reasons to why these exact medicines appears most common in relation to cancer treatment.

### Subset of 10 most prevalent medicines

T

```{r}

# Making list for subsetting cancer data based on drug prevalence
Prevalent_10_medicine_names <- cancer_data |>
  # Counting the medications and sort them in descending order
  group_by(ID) |>
  
  summarise(Proportion = n() / nrow(cancer_data)) |>
  
  ungroup() |>
  
  arrange(desc(Proportion)) |>
  
  slice_head(n = 10)


# Making subset of cancer data for 10 most prevalent drugs
Most_prevalent_medicines <- cancer_data |>
  
  # Return all rows from list of top 10 which matches in cancer data by "medicine name"
  semi_join(Prevalent_10_medicine_names, by = "ID")

```

## Relation to side effects

```{r}

Most_prevalent_medicines |>
  group_by(Medicine_Name) |> 
  distinct(Count_Side_Effects, .keep_all = TRUE) |>
  ggplot(aes(x = Medicine_Name, 
             y = Count_Side_Effects, 
             fill=Administration_type)) + 
  geom_bar(stat= 'identity') + 
  labs(x = "Drug name",
       y = "Number of side effects") + 
  ggtitle("Relationship between side effects and ten most commmon cancer drugs") +
  theme_minimal() +
  guides(fill=guide_legend(title="Adimnistration type")) 

# gøre med ID og så rename akxe med mediicn navne 

```

## Relation to reviews

The relationship between the most common cancer drugs and the dominating review is investigated. This is done for the ID of each drug in case of drugs with the same name appearing multiple times. The investigating is done by creating a subset only containing the three variables of interest; ID, medicine name, and classification of review.

```{r}

Most_prevalent_medicines |>
  group_by(ID) |> 
  distinct(ID, Medicine_Name, Classification_Review) |>
  arrange(Classification_Review) |>
  head(10)

```

## 
